Sweat electrolytes and CFTR activity in the era of CFTR modulators

### 2024-11-01 Edith Zemanick/Sweat Test/sweat_test_analysis.qmd
Update sweat_test_analysis.qmd

chec$Diagnosis <- "CF"

@@

write.csv(df, "./Data_Cleaned/final_analysis_dataset.csv", row.names = F, na = "")

@@

```{r}
df %>%
  filter(Diagnosis == "CF") %>%
  mutate(
    `Age group` = cut(Age.at.Test.in.Years, c(-Inf, 18, Inf), right = F),
    `Cl < 60` = Cl < 60
  ) %>%
  select(Na, Cl, TotalGenotypeFunction, `Cl < 60`, `Age group`) %>%
  tbl_summary(by = `Age group`, missing_text = "Missing") %>%
  add_p()
```

>>>>

chec$Diagnosis <- "Cystic Fibrosis"

@@

write.csv(df, "./Data_Cleaned/final_analysis_dataset.csv",
  row.names = F, na = ""

@@

```{r}
df %>%
  filter(Diagnosis == "Cystic Fibrosis") %>%
  mutate(
    `Age group` = cut(Age.at.Test.in.Years, c(-Inf, 18, Inf), right = F),
    `Cl < 60` = Cl < 60
  ) %>%
  select(Na, Cl, TotalGenotypeFunction, `Cl < 60`, `Age group`) %>%
  tbl_summary(by = `Age group`, missing_text = "Missing") %>%
  add_p()
```
